Chapter 4: Binocular combination in the Autonomic Nervous System

### 2024-01-12 manuscript.Rmd
Modified unzipping command

         # then unzip the tar file
         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir))

@@

         # then unzip the tar file
         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir))

@@

         # then unzip the tar file
         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir))

@@

         # then unzip the tar file
         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir))

>>>>

         # then unzip the tar file
         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir,'P',600+participant))

@@

         # then unzip the tar file
         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir,'P',500+participant))

@@

         # then unzip the tar file
         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir,'P',700+participant))

@@

         # then unzip the tar file
         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir,'P',300+participant))
